Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation-extrapolation capacity validation

### 2022-10-19 Article.tex
Starting updating MZA model

%-------------------------------------------------------------------------
\subsection{Modified Zerilli-Armstrong model\label{sec:MZA}}
%-------------------------------------------------------------------------

As mentioned earlier, Johnson-Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately.
Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli-Armstrong (ZA) model \cite{Hull-2011}.
But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
\begin{equation}
\label{eq:MZA-model}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon^p}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material. The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is sumarized as following.

>>>>

%-------------------------------------------------------------------------
\subsection{Modified Zerilli-Armstrong model\label{sec:MZA}}
%-------------------------------------------------------------------------
\OP{This introduction paragraph is entirely copied from the WJET publication}
As mentioned earlier, Johnson-Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately.
Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli-Armstrong (ZA) model \cite{Hull-2011}.
But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
\begin{equation}
\label{eq:MZA-model}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon^p}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material. The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is sumarized as following.
